---
title: "GSoC-R 2018 Test Answer"
output: html_notebook
---

Easy: Write code to plot the points tagged as being outlying by the current diagnostic methods in quokar, using ah or ais data provided with the package.

We use ais data as real data example to tag the outliers in QR model.

\item absolute residual and robust distance method:

```{r}
library(quokar)
library(tidyverse)
library(quantreg)
library(gridExtra)
ais_female <- ais %>% filter(Sex == 1)
quantiles <- c(0.1, 0.5, 0.9)
rq_object <- rq(BMI ~ LBM + Bfat, data = ais_female, tau = quantiles)
dis <- frame_distance(rq_object, tau = quantiles)
distance <- dis[[1]]
cutoff_v <- dis[[2]]
cutoff_h <- dis[[3]]
n <- nrow(ais_female)
case <- rep(1:n, length(quantiles))
distance <- cbind(case, distance)
distance1 <- distance %>% filter(tau_flag == 'tau0.1')
p1 <- ggplot(distance1, aes(x = rd, y = residuals)) +
        geom_point()+
        geom_hline(yintercept = cutoff_h[1], colour = 'red') +
        geom_vline(xintercept = cutoff_v, colour = 'red') +
        geom_text(data = subset(distance1, residuals > cutoff_h[1]|rd > cutoff_v), 
            aes(label = case), hjust = 0, vjust = 0) +
        xlab("Robust distance") +
        ylab("|Residuals|") +
        theme(aspect.ratio = 1)
distance2 <- distance %>% filter(tau_flag == 'tau0.5')
p2 <- ggplot(distance2, aes(x = rd, y = residuals)) +
        geom_point()+
        geom_hline(yintercept = cutoff_h[2], colour = 'red') +
        geom_vline(xintercept = cutoff_v, colour = 'red') +
        geom_text(data = subset(distance1, residuals > cutoff_h[2]|rd > cutoff_v), 
            aes(label = case), hjust = 0, vjust = 0) +
        xlab("Robust distance") +
        ylab("|Residuals|")+
        theme(aspect.ratio = 1)
distance3 <- distance %>% filter(tau_flag == 'tau0.9')
p3 <- ggplot(distance3, aes(x = rd, y = residuals)) +
        geom_point()+
        geom_hline(yintercept = cutoff_h[3], colour = 'red') +
        geom_vline(xintercept = cutoff_v, colour = 'red') +
        geom_text(data = subset(distance1, residuals > cutoff_h[3]|rd > cutoff_v), 
            aes(label = case), hjust = 0, vjust = 0) +
        xlab("Robust distance") +
        ylab("|Residuals|")+
        theme(aspect.ratio = 1)
grid.arrange(p1, p2, p3, ncol = 3)
```

\item General Cook' distance:

```{r}
y <- ais_female$BMI
x <- cbind(1, ais_female$LBM, ais_female$Bfat)
cook_distance <- frame_mle(y, x, method = "cook.distance", tau = quantiles)
frame_cook <- data.frame(case, cook_distance)
ggplot(frame_cook, aes(x = case, y = value)) +
  geom_point() +
  geom_text(data = subset(frame_cook, value > 
                            mean(value) + 2*sd(value)),
            aes(label = case)) +
  facet_wrap(~variable, scales = "free") +
  xlab("Case") +
  ylab("Cook's distance") +
  theme(aspect.ratio = 1)
```

\item Likelihood distance:

```{r}
qd_distance <- frame_mle(y, x, method = "qfunction", tau = quantiles)
frame_qd <- data.frame(case, qd_distance)
ggplot(frame_qd, aes(x = case, y = value)) +
  geom_point() +
  geom_text(data = subset(frame_qd, value > 
                            mean(value) + sd(value)),
            aes(label = case)) +
  facet_wrap(~variable, scales = "free") +
  xlab("Case") +
  ylab("Likelihood distance") +
  theme(aspect.ratio = 1)
```

\item Mean posterior probability:

```{r}
mp <- frame_bayes(y, x, M = 500, burn = 100, method = "bayes.prob", tau = quantiles)
frame_prob <- data.frame(case, mp)
ggplot(frame_prob, aes(x = case, y = value)) +
  geom_point() +
  geom_text(data = subset(frame_prob, value > 
                            mean(value) + sd(value)),
            aes(label = case)) +
  facet_wrap(~variable, scales = "free") +
  xlab("Case") +
  ylab("Mean posterior probability") +
  theme(aspect.ratio = 1)
```

\item Kullback-Leibler divergence

```{r}
kl <- frame_bayes(y, x, M = 500, burn = 100, method = "bayes.kl", tau = quantiles)
frame_kl <- data.frame(case, mp)
ggplot(frame_prob, aes(x = case, y = value)) +
  geom_point() +
  geom_text(data = subset(frame_kl, value > 
                            mean(value) + sd(value)),
            aes(label = case)) +
  facet_wrap(~variable, scales = "free") +
  xlab("Case") +
  ylab("Kullback-Leibler divergence") +
  theme(aspect.ratio = 1)
```


(Medium) Make plots illustrating the simplex algorithm or interior point algorithm for estimating linear quantile regression parameters.

```{r}
rq_br <- rq(BMI ~ LBM + Bfat, method = 'br', data = ais_female)
obs <- frame_br(rq_br, tau = quantiles)$all_observation
choose <- frame_br(rq_br, tau = quantiles)$fitting_point
ggplot(obs,
 aes(x=value, y=obs[,2])) +
 geom_point(alpha = 0.1) +
 ylab('y') +
 xlab('x') +
 facet_wrap(~variable, scales = "free_x", ncol = 2) +
 geom_point(data = choose, aes(x = x, y = y,
                                      group = tau_flag,
                                      colour = tau_flag,
                               shape = tau_flag))+
 theme(aspect.ratio = 1)
```

(Hard) Make plots illustrating the interior point algorithm for estimating non-linear quantile regression parameters.

```{r}
x <- rep(1:25, 20)
y <- SSlogis(x, 10, 12, 2) * rnorm(500, 1, 0.1)
Dat <- data.frame(x = x, y = y)
formula <- y ~ SSlogis(x, Aysm, mid, scal)
obs_nlrq <- frame_nlrq(formula, data = Dat, tau = c(0.1, 0.5, 0.9))
weights <- obs_nlrq$weights
obs <- data.frame(Dat, weights)
obs_f <- obs %>% gather(tau_flag, value, -x, -y)
ggplot(obs_f, aes(x = x, y = y)) +
 geom_point(aes(size = value)) +
 geom_point(data = subset(obs_f, value > mean(value) + 0.1*sd(value)), aes(colour = tau_flag)) +
 facet_wrap(~tau_flag) +
 theme(aspect.ratio = 1)
```











